---
title: "knitxl: Build an Excel Report from an Rmd File"
author: Denis Dreano
date: 2023-07-26
---

# Introduction {ws_name=intro}

`knitxl` is an R package that an turn an _Rmarkdown_ file into an _XLSX_
spreadsheet report. 

You can install `knitxl` from CRAN:

```{r, eval=FALSE}
install.packages("knitxl")
```

You can then knit an RMD file to XLSX simply by using the `knitxl()` function:

```{r, eval=FALSE}
library(knitxl)
knitxl("path/to/my_rmd_file.Rmd")
```

This will create an excel file in `path/to/my_rdm_file.xlsx`

# Markdown Support

`knitxl` currently supports the following markdown syntax:

## Headers

## Inline Syntax

italic, bold, bold-italic, links, code, strikethrough

## Block Syntax

code blocks

blockquotes


## Lists

numbered, bullet

## Images

## Rules


# Create a New Spreadsheet







# R Code {ws_name=code}

## Executing Inline Code



## Executing Code Chunks

echo, include, 

error warnings messages

rendering data.frames, vector, prints, 

plots (fig.width, ...)






# Customizing `knitxl` {ws_name=customize}

## Styling


## Custom renderers

